---
title: "Physician NPI Lookup"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(npi)
library(DT)
library(tidyverse)
```

Sidebar {.sidebar}
---
### File Upload
Upload a CSV file containing physicians' first names, last names, and zip codes. The file should have columns named 'first_name', 'last_name', and 'zip_code'.

```{r}
radioButtons("searchType", "Search by:",
             choices = list("Names and Zip Codes from File" = "file",
                            "Zip Codes Only" = "zip"),
             inline = TRUE)

conditionalPanel(
  condition = "input.searchType == 'file'",
  fileInput("file1", "Choose CSV File",
            accept = c("text/csv",
                       "text/comma-separated-values,text/plain",
                       ".csv")),
  checkboxInput("header", "Header", TRUE)
)

conditionalPanel(
  condition = "input.searchType == 'zip'",
  textAreaInput("zipCodes", "Enter Zip Codes (comma separated):", "")
)

```

Column {data-width=350}
---
### Uploaded CSV Contents
View the contents of the uploaded CSV file.

```{r}
renderDT({
  req(input$searchType)
  if (input$searchType == "file") {
    req(input$file1)
    df <- read.csv(input$file1$datapath, header = input$header)
  } else {
    req(input$zipCodes)
    zipCodes <- strsplit(input$zipCodes, ",")[[1]]
    zipCodes <- trimws(zipCodes)
    df <- data.frame(zip_code = zipCodes)
  }
  datatable(df)
})

```


Column
---

### NPI Results
The table below will display the uploaded data along with the corresponding NPIs for each physician.

```{r}
renderDT({
  req(input$searchType)
  results <- data.frame()
  if (input$searchType == "file") {
    req(input$file1)
    df <- read.csv(input$file1$datapath, header = input$header)
    if ("first_name" %in% colnames(df) && "last_name" %in% colnames(df) && "zip_code" %in% colnames(df)) {
      results <- apply(df, 1, function(row) {
        npi_res <- tryCatch({
          npi_search(first_name = row["first_name"], last_name = row["last_name"], postal_code = row["zip_code"])
        }, error = function(e) {
          return(data.frame())
        })
        if (nrow(npi_res) > 0) {
          npi_res$first_name <- row["first_name"]
          npi_res$last_name <- row["last_name"]
          npi_res$zip_code <- row["zip_code"]
          return(npi_res)
        } else {
          return(data.frame(first_name = row["first_name"], last_name = row["last_name"], zip_code = row["zip_code"], number = NA))
        }
      }) %>% do.call(rbind, .)
    } else {
      stop("The uploaded file must contain 'first_name', 'last_name', and 'zip_code' columns.")
    }
  } else {
    req(input$zipCodes)
    zipCodes <- strsplit(input$zipCodes, ",")[[1]]
    zipCodes <- trimws(zipCodes)
    results <- lapply(zipCodes, function(zip) {
      npi_res <- tryCatch({
        npi_search(postal_code = zip)
      }, error = function(e) {
        return(data.frame())
      })
      if (nrow(npi_res) > 0) {
        return(npi_res)
      } else {
        return(data.frame(zip_code = zip, npi = NA))
      }
    }) %>% 
    do.call(rbind, .) %>% 
    dplyr::select(npi) %>%
    mutate(
        Zip = input$zip
    )
  }
  datatable(results)
})

```
